Bow shocks, bow waves, and dust waves. III. Diagnostics

### 2019-03-18 papers/Papers1234/sec-observational-diagnostics.tex
Start on mass loss section of Paper III

Third method used by \citet{Gvaramadze:2012a}, relies on measurements
of \hii{} region and bow. Only works for isolated stars.

Mass loss rates - starting from \citet{Kobulnicky:2010a}

\subsection{Mass loss determination from the \(\tau\)--\(\eta\shell\) diagram}
\label{sec:mass-loss-determ}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
  \caption{Wind mass-loss rates as a function of stellar luminosity,
    derived from (a)~our trapped energy/momentum method and (b)~the
    grain emissivity method of \citet{Kobulnicky:2018a}, with
    corrections as described in our Appendix~\ref{app:bow-shock-data}.
    Circle symbols show the sources from K18, colored according to the
    stellar effective temperature (see key at far right). In panel a,
    squares show two of our additional sources
    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
    given for sources that lie close to the radiation-supported line
    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
    symbols and downward-pointing arrows.  Sources that lie less than
    a factor of three above the line have enhanced downward
    uncertainties and are also shown by slightly fainter symbols.  For
    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
    luminosities of the triple OB system Aa, Ab, and B
    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
    the luminosity of only the most massive component Aa.  Lines show
    the predictions of stellar wind models: red lines are the commonly
    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
    (dashed), and supergiants (dotted), while black lines show
    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
    mass-loss measurements from NUV lines for weak-wind O~dwarfs
    \citep{Marcolino:2009a}, while the green plus symbol shows the
    measurement from infrared H recombination lines for \(\sigma\)~Ori
    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
    to observational uncertainties (lower right) and assumed shell
    parameters (upper left).}
  \label{fig:mass-loss-vs-luminosity}
\end{figure*}

>>>>

Various methods have been proposed to derive stellar wind mass-loss
rates from observations of stellar bow shocks \citetext{for example,
  \citealp{Kobulnicky:2010a, Gvaramadze:2012a, Kobulnicky:2018a}}.  In
this section, we will show how the \(\tau\)--\(\eta\shell\) diagram can be
used to derive the mass-loss rate for bows in the wind-supported
regime.  We then compare our method with the method used by
\citet{Kobulnicky:2018a}, which is a refinement of that originally
proposed in \citet{Kobulnicky:2010a}.  The method used by
\citet{Gvaramadze:2012a} uses combined measurements of the bow shock
and the surrounding \hii{} region.  It has the advantage of depending
on fewer free parameters than the other methods, but can only be used
in the case of isolated stars, whereas the majority of the sources
considered here are in cluster environments.

\subsection{Mass loss determination from the \boldmath \(\tau\)--\(\eta\shell\) diagram}
\label{sec:mass-loss-determ}
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
  \caption{Wind mass-loss rates as a function of stellar luminosity,
    derived from (a)~our trapped energy/momentum method and (b)~the
    grain emissivity method of \citet{Kobulnicky:2018a}, with
    corrections as described in our Appendix~\ref{app:bow-shock-data}.
    Circle symbols show the sources from K18, colored according to the
    stellar effective temperature (see key at far right). In panel a,
    squares show two of our additional sources
    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
    given for sources that lie close to the radiation-supported line
    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
    symbols and downward-pointing arrows.  Sources that lie less than
    a factor of three above the line have enhanced downward
    uncertainties and are also shown by slightly fainter symbols.  For
    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
    luminosities of the triple OB system Aa, Ab, and B
    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
    the luminosity of only the most massive component Aa.  Lines show
    the predictions of stellar wind models: red lines are the commonly
    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
    (dashed), and supergiants (dotted), while black lines show
    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
    mass-loss measurements from NUV lines for weak-wind O~dwarfs
    \citep{Marcolino:2009a}, while the green plus symbol shows the
    measurement from infrared H recombination lines for \(\sigma\)~Ori
    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
    to observational uncertainties (lower right) and assumed shell
    parameters (upper left).}
  \label{fig:mass-loss-vs-luminosity}
\end{figure*}

@@
